---
title: "Exploratory Data Analyses for PER Project"
author: "Ian Kahrilas"
date: "1/21/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
# load in dataset
per_erp <- read_csv("per_erp.csv")
library(pander)
library(ggpubr)
library(car)
library(moments)
```

## Questionnaire Descriptive Statisitcs

```{r descriptive stats on variables of interest}
per_erp %>% 
  summarize("PA Mean" = mean(pos_affectivity, na.rm = TRUE),
            "PA SD" = sd(pos_affectivity, na.rm = TRUE),
            "NA Mean" = mean(neg_affectivity, na.rm = TRUE),
            "NA SD" = sd(neg_affectivity, na.rm = TRUE),
            "StM Mean" = mean(savoring_moment, na.rm = TRUE),
            "StM SD" = sd(savoring_moment, na.rm = TRUE),
            "Anticipating Mean" = mean(anticipating, na.rm = TRUE),
            "Anticipating SD" = sd(anticipating, na.rm = TRUE),
            "Reminiscing Mean" = mean(reminiscing, na.rm = TRUE),
            "Reminiscing SD" = sd(reminiscing, na.rm = TRUE)) %>% 
  pander(split.tables = 200, caption = "PA = Positive Affectivity, NA = Negative Affectivity, StM = Savoring the Moment")
```

## LPP Descriptive Statistics by Block

```{r descriptive statistics for LPP}
per_erp %>% 
  group_by(block) %>% 
  summarize("LPP Mean" = mean(LPP, na.rm = TRUE),
            "LPP SD" = sd(LPP, na.rm = TRUE)) %>% 
  pander()
```

## Positive Affectivity

```{r PA histogram}
per_erp %>% 
  group_by(pid) %>% 
  summarize(pos_affectivity = mean(pos_affectivity, na.rm = TRUE)) %>% 
  ggplot(., (aes(pos_affectivity))) +
    geom_histogram(bins = 15) +
    ggtitle("PA Histogram")
```

```{r PA QQplot}
per_erp %>% 
  group_by(pid) %>% 
  summarize(pos_affectivity = mean(pos_affectivity, na.rm = TRUE)) %>% 
  ggplot(., aes(sample = pos_affectivity)) + 
  stat_qq() +
  stat_qq_line() +
  ggtitle("PA QQPlot")
```

It would appear that there is a slight negative skew to the data, though it does not deviate from a gaussian distribution substantially. Let's confirm with a shapiro-wilk test for normality

```{r shapiro-wilk test for positive affectivity, echo = FALSE}
pid_pa <- per_erp %>% 
  group_by(pid) %>% 
  summarize(pos_affectivity = mean(pos_affectivity, na.rm = TRUE))
shapiro.test(pid_pa$pos_affectivity) %>% 
  pander()
rm(pid_pa)
```

It is not significant, suggesting that the distribution of PA does not significantly deviate from the normal distribution.

## Negative Affectivity

```{r negative affectivity histogram}
per_erp %>% 
  group_by(pid) %>% 
  summarize(neg_affectivity = mean(neg_affectivity, na.rm = TRUE)) %>% 
  ggplot(., (aes(neg_affectivity))) +
    geom_histogram(bins = 15) +
    ggtitle("NA Histogram")
```

```{r negative affectivity qqplot}
per_erp %>% 
  group_by(pid) %>% 
  summarize(neg_affectivity = mean(neg_affectivity, na.rm = TRUE)) %>% 
  ggplot(., aes(sample = neg_affectivity)) + 
  stat_qq() +
  stat_qq_line() +
  ggtitle("NA QQPlot")
```

```{r shapiro-wilk test for NA}
pid_na <- per_erp %>% 
  group_by(pid) %>% 
  summarize(neg_affectivity = mean(neg_affectivity, na.rm = TRUE))
shapiro.test(pid_na$neg_affectivity) %>% 
  pander()
rm(pid_na)
```

NA does not significantly deviate from the normal distribution.

## Savoring the Moment

```{r StM histogram}
per_erp %>% 
  group_by(pid) %>% 
  summarize(savoring_moment = mean(savoring_moment, na.rm = TRUE)) %>% 
  ggplot(., (aes(savoring_moment))) +
    geom_histogram(bins = 25) +
    ggtitle("Savoring the Moment Histogram")
```

```{r StM qqplot}
per_erp %>% 
  group_by(pid) %>% 
  summarize(savoring_moment = mean(savoring_moment, na.rm = TRUE)) %>% 
  ggplot(., aes(sample = savoring_moment)) + 
  stat_qq() +
  stat_qq_line() +
  ggtitle("Savoring the Moment QQPlot")
```
```{r shapiro-wilk test for StM}
pid_StM <- per_erp %>% 
  group_by(pid) %>% 
  summarize(savoring_moment = mean(savoring_moment, na.rm = TRUE))
shapiro.test(pid_StM$savoring_moment) %>% 
  pander()
rm(pid_StM)
```

## LPP

### Histograms, and QQplots for each block
```{r histograms and qqplots for LPP for each block, warning = FALSE}
LPP_by_pid <- per_erp %>% 
  group_by(pid, block) %>% 
  summarize(LPP = mean(LPP, na.rm = TRUE))

LPP_hist_qq <- function(cond, title) {
LPP_by_pid %>% 
  filter(block == cond) %>% 
  gghistogram(., "LPP", title = title) %>% 
    print()
LPP_by_pid %>% 
  filter(block == cond) %>% 
  ggqqplot(., "LPP", title = title)
}

conditions <- unique(LPP_by_pid$block)
cond_names <- c(paste("Negative", c("Decrease", "Increase", "Watch")), "Neutral Watch", paste("Positive", c("Decrease", "Increase", "Watch")))

map2(conditions, cond_names, ~ LPP_hist_qq(cond = .x, title = .y))
```

```{r shapiro-wilk tests for normality}
shapiro_LPP <- function(condition, title) {
result <- shapiro.test(pull(filter(LPP_by_pid, block == condition))) %>% 
  pander(caption = title)
  }
```

```{r negative decrease}
shapiro_LPP("Neg_Dec", "Negative Decrease")
```

```{r negative increase}
shapiro_LPP("Neg_Inc", "Negative Increase")
```

```{r negative watch}
shapiro_LPP("Neg_Watch", "Negative Watch")
```

```{r neutral watch}
shapiro_LPP("Neu_Watch", "Neutral Watch")
```

```{r positive decrease}
shapiro_LPP("Pos_Dec", "Positive Decrease")
```
```{r positive increase}
shapiro_LPP("Pos_Inc", "Positive Increase")
```

```{r positive watch}
shapiro_LPP("Pos_Watch", "Positive Watch")
```

Several of the conditions have LPPs that are non-normally distributed with some outtliers. Let's inspect these extreme cases.

```{r examine extreme cases}
extreme_cases <- function(condition, name) {
(cases <- LPP_by_pid %>% 
  filter(block == condition,
         LPP > 17))
cases %>% 
  select(pid) %>% 
  pull()
}
# this outputs participants that have LPP amplitudes greater than 17, which denote the extreme cases we observed in the histograms and qqplots.
map2(conditions, cond_names, ~ extreme_cases(.x, .y))
```

Our extreme cases are 206201843 and 206201840. Reviewing our EEG trial notes indicates that these two particpants were moving throughout the PER task and produced noisy data. Therefore, they will be removed from the dataset

```{r remove noisy participants}
LPP_pid_rem <- LPP_by_pid %>% 
  filter(!(pid %in% c(206201843, 206201840)))
# re-run normality tests to see what's going on
LPP_hist_qq <- function(cond, title) {
LPP_pid_rem %>% 
  filter(block == cond) %>% 
  gghistogram(., "LPP", title = title) %>% 
    print()
LPP_pid_rem %>% 
  filter(block == cond) %>% 
  ggqqplot(., "LPP", title = title)
}

conditions <- unique(LPP_by_pid$block)
cond_names <- c(paste("Negative", c("Decrease", "Increase", "Watch")), "Neutral Watch", paste("Positive", c("Decrease", "Increase", "Watch")))

map2(conditions, cond_names, ~ LPP_hist_qq(cond = .x, title = .y))
```

```{r shapiro wilk tests with filtered data}
shapiro_LPP <- function(condition, title) {
result <- shapiro.test(pull(filter(LPP_pid_rem, block == condition))) %>% 
  pander(caption = title)
}

shapiro_LPP("Neg_Dec", "Negative Decrease")
```

```{r}
shapiro_LPP("Neg_Inc", "Negative Increase")
```

```{r}
shapiro_LPP("Neg_Watch", "Negative Watch")
```

```{r}
shapiro_LPP("Neu_Watch", "Neutral Watch")
```

```{r}
shapiro_LPP("Pos_Dec", "Positive Decrease")
```

```{r}
shapiro_LPP("Pos_Inc", "Positive Increase")
```

```{r}
shapiro_LPP("Pos_Watch", "Positive Watch")
```

Some are still significantly different from the normal distribution, observation of the more extreme cases in the EEG run notes does not indicate any abnormalities. This indicates that a non-parametric technique, like bootstrapping, should be utilized for tests that assume normal data. 

```{r manipulate the dataset to facilitate bivariate analyses}
per_erp_int <- per_erp %>% 
  select(pid, block, LPP, arousal:valence, anticipating:erq_suppression) %>% 
    filter(!(pid %in% c(206201843, 206201840)))
```

Box and whisker plots for each block

```{r visualize LPP by block}
ggplot(per_erp_int, aes(block, LPP)) +
  geom_boxplot() +
  ggtitle("Average LPP for each block")
```

Scatterplot between the LPP positive watch condition and positive affectivity

```{r positive affectivity and LPP}
per_erp_int %>% 
  filter(block == "Pos_Watch") %>% 
  ggplot(., aes(pos_affectivity, LPP)) +
  geom_point() + 
  geom_smooth(method = "lm") +
  ggtitle("Positive affectivity and LPP in positive watch condition")
```

Scatterplot between the LPP positive increase condition and savoring the moment

```{r savoring the moment and LPP}
per_erp_int %>% 
  filter(block == "Pos_Inc") %>% 
  ggplot(., aes(savoring_moment, LPP)) +
  geom_point() + 
  geom_smooth(method = "lm") +
  ggtitle("Savoring the moment and LPP in the positive increase condition")
```

Scatterplot between LPP and arousal ratings

```{r arousal ratings and LPP}
ggplot(per_erp_int, aes(arousal, LPP)) +
  geom_jitter() + 
  geom_smooth(method = "lm") +
  ggtitle("Arousal ratings and LPP")
```

Scatterplot between LPP and valence ratings

```{r valence ratings and LPP}
ggplot(per_erp_int, aes(valence, LPP)) +
  geom_jitter() + 
  geom_smooth(method = "lm") +
  ggtitle("Valence ratings and LPP")
```

Scatterplot between LPP and dificulty ratings

```{r difficulty ratings and LPP}
ggplot(per_erp_int, aes(difficulty, LPP)) +
  geom_jitter() + 
  geom_smooth(method = "lm") +
  ggtitle("Difficulty ratings and LPP")
```

Derive contrasts between neutral watch and positive watch conditions and observe relationship between this contrast and positive affectivity, which is in line with the study hypothesis that the LPP contrast between the neutral watch and positive watch conditions will be moderated by positive affectivity

```{r pos affectivity contrasts}
pos_watch_contrast <- per_erp_int %>% 
  filter(block == "Neu_Watch") %>%
  rename("LPP_neu_watch" = LPP) %>% 
  select(-block)

tmp <- per_erp_int %>% 
  filter(block == "Pos_Watch") %>% 
  rename("LPP_pos_watch" = LPP) %>% 
  select(pid, LPP_pos_watch)

pos_watch_contrast <- full_join(pos_watch_contrast, tmp, by = "pid") %>% 
  mutate(contrast = LPP_pos_watch - LPP_neu_watch)

ggplot(pos_watch_contrast, aes(pos_affectivity, contrast)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ggtitle("Positive affectivity and the LPP contrast between the neutral watch and positive watch conditions")
```

Derive contrasts between positive watch and positive increase conditions and observe relationship between this contrast and savoring the moment, which is in line with the study hypothesis that the LPP contrast between the positive watch and positive increase conditions will be moderated by savoring the moment.

```{r savoring moment contrasts}
pos_inc_contrast <- per_erp_int %>% 
  filter(block == "Pos_Watch") %>%
  rename("LPP_pos_watch" = LPP) %>% 
  select(-block)

tmp <- per_erp_int %>% 
  filter(block == "Pos_Inc") %>% 
  rename("LPP_pos_inc" = LPP) %>% 
  select(pid, LPP_pos_inc)

pos_inc_contrast <- full_join(pos_inc_contrast, tmp, by = "pid") %>% 
  mutate(contrast = LPP_pos_inc - LPP_pos_watch)

ggplot(pos_inc_contrast, aes(savoring_moment, contrast)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ggtitle("Savoring the moment and the LPP contrast between the positive watch and positive increase conditions")
```