---
title: "Exploratory Data Analysis with Pawpaw Miller"
author: "Ian Kahrilas"
date: "1/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
# load in dataset
per_erp <- read_csv("per_erp.csv")
glimpse(per_erp)
```

# Univariate Analyses

## Variables
The following variables are a part of the dataset used for PER

```{r variables for PER}
names(per_erp)
```
- Block corresponds to the specific regulation/valence condition
- The variables with "LPP" in the name correspond to the occipital parietal component observed across different timepoints. The variable just named "LPP" corresponds to the 400-1000 ms window, which the most commonly occuring window used in the literature and the window used for analyses.
- Difficulty and valence correspond to the rating questions asked of each participant following each regulation block
- Political orientation is a 7-point likert scale assessing ones political beliefs. 1 corresponds to very liberal and 7 corresponds to very conservative. This was included since an article (Tritt et al., 2016) found differences in LPP signal depending on political orientation. These were ultimately never used in analyses.
 - 

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

