---
title: "More Behavior Rating Analyses"
author: "Ian Kahrilas"
date: "5/20/2020"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lmerTest)
library(boot)
library(here)
library(ggpubr)
library(car)
library(emmeans)
library(easystats)
library(welchADF)
library(moments)
library(modelbased)
library(patchwork)
library(report)
library(r2glmm)
library(performance)
library(bootmlm)
# load in data
per_dat <- read_csv(here("data", "created_data", "per_data_analyses_2020_5_19.csv"))

# create dataset with lateralization variable
tmp <- per_dat %>% 
  pivot_longer(c("EPN_left", "EPN_right"), names_to = "lateralization", names_prefix = "EPN_", values_to = "EPN") %>% 
  select(-c(N170_right, N170_left))
tmp2 <- per_dat %>% 
  pivot_longer(c("N170_left", "N170_right"), names_to = "lateralization", names_prefix = "N170_", values_to = "N170") %>% 
  select(pid, block, N170, lateralization)
per_dat_lat <- left_join(tmp, tmp2, by = c("pid", "block", "lateralization")) %>% 
  select(pid:LPP, EPN, N170, lateralization, everything())

# create bilateral EPN and N170 variable to be used in initial analyses
per_dat <- per_dat %>% 
  mutate(N170 = (N170_left + N170_right) / 2,
         EPN = (EPN_left + EPN_right) / 2) %>% 
  select(pid:LPP, N170, EPN, everything())

# summary function to use with bootstrap function
mySumm <- function(x) {
  c(getME(x, "beta"), sigma(x))
}
```

## Valence and difficulty ratings

```{r, message=FALSE, warning=FALSE}
per_dat %>% 
ggplot(., aes(valence, difficulty)) +
  geom_jitter(height = 0.2, width = 0.2) + 
  geom_smooth() +
  ggtitle("Valence and difficulty ratings")

mod_diff_val <- lmer(difficulty ~ valence + (1|pid), data = per_dat)
check_model(mod_diff_val)
summary(mod_diff_val)
mod_diff_val_poly <- lmer(difficulty ~ poly(valence, 2) + (1|pid), data = per_dat)
summary(mod_diff_val_poly) # the polynomial term is non-significant
mod_diff_poisson <- glmer(difficulty ~ poly(valence, 1) + (1|pid), family = "poisson", data = per_dat)
summary(mod_diff_poisson)
compare_performance(mod_diff_val, mod_diff_poisson)
# Covariance preserving residual bootstrap
boo01 <- bootstrap_mer(mod_diff_val, mySumm, type = "residual", nsim = 5000)
# Plot bootstrap distribution of fixed effect
plot(boo01, index = 2)
# Get confidence interval
boot.ci(boo01, index = 2, type = "basic")
```

There is a linear relationship between difficulty and valence, but no polynomial term.

## Valence and arousal

```{r, message=FALSE, warning=FALSE}
per_dat %>% 
ggplot(., aes(valence, arousal)) +
  geom_jitter(width = 0.3, height = 0.3) + 
  geom_smooth() +
#  geom_smooth(method = "lm") +
 # stat_smooth(method = "lm", formula = y ~ poly(x, 2), color = "red") +
  ggtitle("Valence and arousal ratings")

mod_val_arousal <- lmer(arousal ~ poly(valence, 1) + (1|pid), data = per_dat)
check_model(mod_val_arousal, panel = FALSE)
mod_val_arousal_poly <- glmer(valence ~ poly(arousal, 2) + (1|pid), data = per_dat)
anova(mod_val_arousal, mod_val_arousal_poly)
# chisquare test indicates that the polynomial model explains significantly more variance
check_model(mod_val_arousal_poly, panel = FALSE)
summary(mod_val_arousal_poly)
report(mod_val_arousal)
r2beta(mod_val_arousal)

# Covariance preserving residual bootstrap
boo01 <- bootstrap_mer(mod_val_arousal_poly, mySumm, type = "residual", nsim = 5000)
# Plot bootstrap distribution of fixed effect
plot(boo01, index = 3)
# Get confidence interval
boot::boot.ci(boo01, index = 3, type = "basic")
```

There is a strong curvilinear relationship between the two. 

## Arousal and difficulty ratings

```{r, message=FALSE, warning=FALSE}
per_dat %>% 
ggplot(., aes(arousal, difficulty)) +
  geom_jitter(height = 0.3, width = 0.3) + 
  stat_smooth() +
  ggtitle("Arousal and difficulty ratings")

ar_diff <- lmer(difficulty ~ arousal + (1|pid), data = per_dat)
check_model(ar_diff)
summary(ar_diff)
# significant linear relationship between difficulty and arousal
ar_diff_poly <- lmer(difficulty ~ poly(arousal, 2) + (1|pid), data = per_dat)
check_model(ar_diff_poly)
summary(ar_diff_poly)
# significant polynomial relationship between difficulty and arousal
anova(ar_diff_poly, ar_diff)
# significant chi-square test signifies that polynomial model is a superior fit
ar_diff_poisson <- glmer(difficulty ~ arousal + (1|pid), family = "poisson", data = per_dat)
summary(ar_diff_poisson)
ar_diff_poly_poisson <- glmer(difficulty ~ poly(arousal, 2) + (1|pid), family = "poisson", data = per_dat)
summary(ar_diff_poisson)
compare_performance(ar_diff,
                    ar_diff_poly,
                    ar_diff_poisson,
                    ar_diff_poly_poisson,
                    rank = TRUE)
```

## Behavioral rating score relations with block

```{r}
# single emm model for all conditions
per_dat_cond <- per_dat %>% 
  separate(block, c("valence_condition", "regulation_condition"), "_") %>% 
  mutate(valence_condition = if_else(valence_condition == "Neg", "Negative",
                           if_else(valence_condition == "Pos", "Positive", "Neutral")),
         regulation_condition = if_else(regulation_condition == "Dec", "Decrease",
                              if_else(regulation_condition == "Inc", "Increase", "Watch")))

# arousal comparisons
reg_mod_ar <- lmer(arousal ~ valence_condition * regulation_condition + (1|pid), data = per_dat_cond)
emmeans(reg_mod_ar, pairwise ~ valence_condition | regulation_condition)
emmeans(reg_mod_ar, pairwise ~ regulation_condition | valence_condition)
check_model(reg_mod_ar)
# valence comparisons
reg_mod_val <- lmer(valence ~ valence_condition * regulation_condition + (1|pid), data = per_dat_cond)
emmeans(reg_mod_val, pairwise ~ valence_condition | regulation_condition)
emmeans(reg_mod_val, pairwise ~ regulation_condition | valence_condition)
# difficulty comparisons
reg_mod_diff <- lmer(difficulty ~ valence_condition * regulation_condition + (1|pid), data = per_dat_cond)
emmeans(reg_mod_diff, pairwise ~ valence_condition | regulation_condition)
emmeans(reg_mod_diff, pairwise ~ regulation_condition | valence_condition)

# visualization - arousal
per_dat %>% 
  ggplot(aes(block, arousal)) +
  geom_boxplot() + 
  ggtitle("Arousal Ratings by Block")

# visualization - valence
per_dat %>% 
  ggplot(aes(block, valence)) +
  geom_boxplot() +
  ggtitle("Valence Ratings by Block")

# visualization - difficulty
per_dat %>% 
  ggplot(aes(block, difficulty)) +
  geom_boxplot() +
  ggtitle("Difficulty Ratings by Block")
```

## Relations between positive affectivity and behavioral ratings

````{r}
#---- POS_AFFECTIVITY
## arousal
per_dat$block <- relevel(factor(per_dat$block), "Neu_Watch")
mod_arousal_pa <- lmer(arousal ~ pos_affectivity + (1|pid), data = per_dat)
check_model(mod_arousal_pa, panel = FALSE)
summary(mod_arousal_pa)
## interaction between positive affectivity and block for arousal
mod_arousal_pa_int <- lmer(arousal ~ block * pos_affectivity + (1|pid), data = per_dat)
check_model(mod_arousal_pa_int, panel = FALSE)
summary(mod_arousal_pa_int)
# There is no interaction term
## valence
mod_valence_pa <- lmer(valence ~ pos_affectivity + (1|pid), data = per_dat)
check_model(mod_valence_pa, panel = FALSE)
summary(mod_valence_pa)
# no relationship
## interaction between positive affectivity and block for valence
mod_valence_pa_int <- lmer(valence ~ block * pos_affectivity + (1|pid), data = per_dat)
check_model(mod_valence_pa_int, panel = FALSE)
summary(mod_valence_pa_int)
# there is an interaction term, though no direct relationship between PA and valence
```

## Relations between savoring the moment and behavioral ratings

```{r}
#---- SAVORING THE MOMENT
## arousal
per_dat$block <- relevel(factor(per_dat$block), "Pos_Watch")
mod_arousal_stm <- glmer(arousal ~ savoring_moment + (1|pid), data = per_dat)
check_model(mod_arousal_stm, panel = FALSE)
summary(mod_arousal_stm)
# no relationship between savoring the moment and arousal
## interaction between positive affectivity and block for arousal
mod_arousal_stm_int <- lmer(arousal ~ block * savoring_moment + (1|pid), data = per_dat)
check_model(mod_arousal_stm_int, panel = FALSE)
summary(mod_arousal_stm_int)
# There is no interaction term
## valence
mod_valence_stm <- lmer(valence ~ savoring_moment + (1|pid), data = per_dat)
check_model(mod_valence_stm, panel = FALSE)
summary(mod_valence_stm)
# no relationship
## interaction between positive affectivity and block for valence
mod_valence_stm_int <- lmer(valence ~ block * savoring_moment + (1|pid), data = per_dat)
check_model(mod_valence_stm_int, panel = FALSE)
summary(mod_valence_stm_int)
# there is no interaction term
```

## For fun, take a look at depression

```{r}
#---- DEPRESSION
# arousal
## Neutral watch reference group
per_dat$block <- relevel(factor(per_dat$block), "Neu_Watch")
mod_arousal_dep <- lmer(arousal ~ depression + (1|pid), data = per_dat)
check_model(mod_arousal_dep, panel = FALSE)
summary(mod_arousal_dep)
# no relationship between depression and arousal
## interaction between depression and block for arousal
mod_arousal_dep_int <- lmer(arousal ~ block * depression + (1|pid), data = per_dat)
check_model(mod_arousal_dep_int, panel = FALSE)
summary(mod_arousal_dep_int)
# There is no interaction term

# positive watch reference group
per_dat$block <- relevel(factor(per_dat$block), "Pos_Watch")
mod_arousal_dep_int <- lmer(arousal ~ block * depression + (1|pid), data = per_dat)
check_model(mod_arousal_dep_int, panel = FALSE)
summary(mod_arousal_dep_int)

# negative watch reference group
per_dat$block <- relevel(factor(per_dat$block), "Neg_Watch")
mod_arousal_dep_int <- lmer(arousal ~ block * depression + (1|pid), data = per_dat)
check_model(mod_arousal_dep_int, panel = FALSE)
summary(mod_arousal_dep_int)

# valence
## Neutral watch reference group
per_dat$block <- relevel(factor(per_dat$block), "Neu_Watch")
mod_valence_dep <- lmer(valence ~ depression + (1|pid), data = per_dat)
check_model(mod_valence_dep, panel = FALSE)
summary(mod_valence_dep)
# no relationship between depression and arousal
## interaction between depression and block for arousal
mod_valence_dep_int <- lmer(valence ~ block * depression + (1|pid), data = per_dat)
check_model(mod_valence_dep_int, panel = FALSE)
summary(mod_valence_dep_int)
# There is no interaction term

# positive watch reference group
per_dat$block <- relevel(factor(per_dat$block), "Pos_Watch")
mod_valence_dep_int <- lmer(valence ~ block * depression + (1|pid), data = per_dat)
check_model(mod_arousal_dep_int, panel = FALSE)
summary(mod_arousal_dep_int)

# negative watch reference group
per_dat$block <- relevel(factor(per_dat$block), "Neg_Watch")
mod_valence_dep_int <- lmer(valence ~ block * depression + (1|pid), data = per_dat)
check_model(mod_arousal_dep_int, panel = FALSE)
summary(mod_arousal_dep_int)
```





```{r}
#--- ERQ SUBSCALES - LOOK AT VALENCE TOO
# reappraisal arousal
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_arousal_reappraisal <- lmerTest::lmer(arousal ~ erq_reappraisal + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_reappraisal)
mod_arousal_reappraisal_block <- lmerTest::lmer(arousal ~ block*erq_reappraisal + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Neg_Watch", "Neg_Inc", "Neg_Dec")))
summary(mod_arousal_reappraisal_block)
# nothing here
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_arousal_reappraisal_block_pos <- lmerTest::lmer(arousal ~ block*erq_reappraisal + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Pos_Watch", "Pos_Inc", "Pos_Dec")))
summary(mod_arousal_reappraisal_block_pos)
## interactin for erq with pos_dec vs. watch and arousal
# reappraisal valence
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_valence_reappraisal <- lmerTest::lmer(valence ~ erq_reappraisal + (1|pid), data = per_erp_filter_lat)
summary(mod_valence_reappraisal)
mod_valence_reappraisal_block <- lmerTest::lmer(valence ~ block*erq_reappraisal + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Neg_Watch", "Neg_Inc", "Neg_Dec")))
summary(mod_arousal_reappraisal_block)
# interaction between negative increase and erq suppression - not what would be suspected
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_valence_reappraisal_block_pos <- lmerTest::lmer(valence ~ block*erq_reappraisal + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Pos_Watch", "Pos_Inc", "Pos_Dec")))
summary(mod_valence_reappraisal_block_pos)
# intearction between positive decrease and erq reappraisal
## interactin for erq with pos_dec vs. watch and arousal

# suppression - LOOK AT VALENCE???
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_arousal_reappraisal <- lmerTest::lmer(arousal ~ erq_suppression + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_reappraisal)
mod_arousal_reappraisal_block <- lmerTest::lmer(arousal ~ block*erq_suppression + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Neg_Watch", "Neg_Inc", "Neg_Dec")))
summary(mod_arousal_reappraisal_block)
# Interaction between neg inc vs. neg watch and arousal by suppression - doesn't make a whole lot of sense
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_arousal_reappraisal_block_pos <- lmerTest::lmer(arousal ~ block*erq_suppression + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Pos_Watch", "Pos_Inc", "Pos_Dec")))
summary(mod_arousal_reappraisal_block_pos)
# nothing
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_arousal_reappraisal <- lmerTest::lmer(valence ~ erq_suppression + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_reappraisal)
mod_arousal_reappraisal_block <- lmerTest::lmer(arousal ~ block*erq_suppression + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Neg_Watch", "Neg_Inc", "Neg_Dec")))
summary(mod_arousal_reappraisal_block)
# Interaction between neg inc vs. neg watch and arousal by suppression - doesn't make a whole lot of sense
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_arousal_reappraisal_block_pos <- lmerTest::lmer(arousal ~ block*erq_suppression + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Pos_Watch", "Pos_Inc", "Pos_Dec")))
summary(mod_arousal_reappraisal_block_pos)
# nothing

## suppression and valence
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_valence_reappraisal <- lmerTest::lmer(valence ~ erq_suppression + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_reappraisal)
mod_valence_reappraisal_block <- lmerTest::lmer(valence ~ block*erq_suppression + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Neg_Watch", "Neg_Inc", "Neg_Dec")))
summary(mod_valence_reappraisal_block)
# Interaction between neg inc vs. neg watch and arousal by suppression - doesn't make a whole lot of sense

#----- TMMS Subscales
## repair
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neu_Watch")
arousal_repair <- lmerTest::lmer(arousal ~ tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(arousal_repair)
# nothing
arousal_repair_block <- lmerTest::lmer(arousal ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(arousal_repair_block)
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
arousal_repair_block_neg <- lmerTest::lmer(arousal ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(arousal_repair_block_neg)
# interactions between TMMS subscale and neg_watch vs. Neg_dec - cool
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
arousal_repair_block_pos <- lmerTest::lmer(arousal ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(arousal_repair_block_pos)
# nothing for positive
# look at valence 
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neu_Watch")
valence_repair <- lmerTest::lmer(valence ~ tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(valence_repair)
# nothing
valence_repair_block <- lmerTest::lmer(valence ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(valence_repair_block)
# interactions between passive watch conditions here
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
valence_repair_block_neg <- lmerTest::lmer(valence ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(valence_repair_block_neg)
# interactions here between neg ince vs. neg watch and tmms repair
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
valence_repair_block_pos <- lmerTest::lmer(valence ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(valence_repair_block_pos)
# nothing here of interest
## attention
## suppression
```
