---
title: "More Behavior Rating Analyses"
author: "Ian Kahrilas"
date: "5/20/2020"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lmerTest)
library(here)
library(ggpubr)
library(car)
library(emmeans)
library(easystats)
library(welchADF)
library(moments)
library(modelbased)
library(patchwork)
library(report)
library(r2glmm)
library(performance)
# load in data
per_dat <- read_csv(here("data", "created_data", "per_data_analyses_2020_5_19.csv"))

# create dataset with lateralization variable
tmp <- per_dat %>% 
  pivot_longer(c("EPN_left", "EPN_right"), names_to = "lateralization", names_prefix = "EPN_", values_to = "EPN") %>% 
  select(-c(N170_right, N170_left))
tmp2 <- per_dat %>% 
  pivot_longer(c("N170_left", "N170_right"), names_to = "lateralization", names_prefix = "N170_", values_to = "N170") %>% 
  select(pid, block, N170, lateralization)
per_dat_lat <- left_join(tmp, tmp2, by = c("pid", "block", "lateralization")) %>% 
  select(pid:LPP, EPN, N170, lateralization, everything())

# create bilateral EPN and N170 variable to be used in initial analyses
per_dat <- per_dat %>% 
  mutate(N170 = (N170_left + N170_right) / 2,
         EPN = (EPN_left + EPN_right) / 2) %>% 
  select(pid:LPP, N170, EPN, everything())
```

## Valence and difficulty ratings

```{r, message=FALSE, warning=FALSE}
per_dat %>% 
ggplot(., aes(valence, difficulty)) +
  geom_jitter(height = 0.2, width = 0.2) + 
  geom_smooth() +
  ggtitle("Valence and difficulty ratings")

mod_diff_val <- lmer(difficulty ~ valence + (1|pid), data = per_dat)
summary(mod_diff_val)
mod_diff_val_poly <- lmer(difficulty ~ poly(valence, 2) + (1|pid), data = per_dat)
summary(mod_diff_val_poly) # the polynomial term is non-significant
mod_diff_poisson <- glmer(difficulty ~ poly(valence, 2) + (1|pid), family = "quasipoisson", data = per_dat)
summary(mod_diff_poisson)
check_model(mod_diff_poisson)
check_overdispersion(mod_diff_poisson)

```

There is a linear relationship between difficulty and valence, but no polynomial term.

## Valence and arousal

```{r, message=FALSE, warning=FALSE}
per_dat %>% 
ggplot(., aes(valence, arousal)) +
  geom_jitter(width = 0.3, height = 0.3) + 
  geom_smooth() +
#  geom_smooth(method = "lm") +
 # stat_smooth(method = "lm", formula = y ~ poly(x, 2), color = "red") +
  ggtitle("Valence and arousal ratings")

mod_val_arousal <- lmer(arousal ~ poly(valence, 1) + (1|pid), data = per_dat)
check_model(mod_val_arousal, panel = FALSE)
mod_val_arousal_poly <- glmer(valence ~ poly(arousal, 2) + (1|pid), data = per_dat)
check_model(mod_val_arousal_poly, panel = FALSE)
summary(mod_val_arousal)
report(mod_val_arousal)
r2beta(mod_val_arousal)

hist(per_dat$arousal)
```

It looks like there is a strong curvilinear relationship between the two. 

```{r, message=FALSE, warning=FALSE}

```

The MLM analysis confirms this relationship.

## Arousal and difficulty ratings

```{r, message=FALSE, warning=FALSE}
per_erp_filter_lat %>% 
  filter(lateralization == "avg") %>% 
ggplot(., aes(arousal, difficulty)) +
  geom_jitter(height = 0.3, width = 0.3) + 
  stat_smooth() +
  ggtitle("Arousal and difficulty ratings")
```

There is perhaps a curvilinear relationship. Let's model a locally weighted (green) and polynomial regression (red) line on the plot to see what the relationship is, and how well the polynomial regression line fits compared to the locally weighted one.

```{r, message=FALSE, warning=FALSE}
ggplot(filter(per_erp_filter_lat, lateralization == "avg"), aes(arousal, difficulty)) +
  geom_jitter(height = 0.3, width = 0.3) + 
  geom_smooth(color = "green", alpha = 0.2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 2), color = "red", alpha = 0.2) +
  ggtitle("Arousal and difficulty ratings")
```

It looks like the curvilnear relationship may be a good fit. Let's test it with an MLM analysis

```{r, warning=FALSE, message=FALSE}
mod_diff_arousal <- lmerTest::lmer(difficulty ~ poly(arousal, 2) + (1|pid), data = per_erp_filter_lat %>% filter(lateralization == "avg"))
summary(mod_diff_arousal)
r2beta(mod_diff_arousal)
```

Indeed, the results indicated that the relationship is curvilinear.

Exploration of traits and average EEG components collapsed across all groups.
```{r trait and average eeg exploration}
stm_lpp <- lmerTest::lmer(LPP ~ savoring_moment + lateralization + (1|pid), data = per_erp_filter_lat %>% filter(lateralization %in% c("left", "right")))
summary(stm_lpp)
pa_lpp <- lmerTest::lmer(LPP ~ pos_affectivity + (1|pid), data = per_erp_filter_lat %>% filter(lateralization %in% c("right", "left")))
summary(pa_lpp)
stm_epn <- lmerTest::lmer(EPN ~ savoring_moment + lateralization + (1|pid), data = per_erp_filter_lat %>% filter(lateralization %in% c("left", "right")))
summary(stm_epn)
pa_epn <- lmerTest::lmer(EPN ~ pos_affectivity + (1|pid), data = per_erp_filter_lat %>% filter(lateralization %in% c("left", "right")))
summary(pa_epn)
# revised lpp
stm_lpp_rev <- lmerTest::lmer(LPP ~ savoring_moment + (1|pid), data = per_erp_rev)
summary(stm_lpp_rev)
pa_lpp_rev <- lmerTest::lmer(LPP ~ pos_affectivity + (1|pid), data = per_erp_rev)
summary(pa_lpp_rev)
# right front
stm_front <- lmerTest::lmer(front_avr ~ savoring_moment*lateralization + (1|pid), data = per_erp_filter_lat %>%  filter(lateralization %in% c("right", "left")))
summary(stm_front)

stm_right_front <- lmerTest::lmer(front_avr ~ depression + (1|pid), data = per_erp_filter_lat %>% filter(lateralization %in% c("right")))
summary(stm_right_front)
```

# check out arousal/valence predicted by block/personality traits
## CONTINUE WITH THIS SECTION
```{r}
#---- POS_AFFECTIVITY
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neu_Watch")
mod_arousal_pa <- lmerTest::lmer(arousal ~ block * pos_affectivity + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_pa)
## interaction between arousal ratings and positive affecitivity
mod_valence_pa <- lmerTest::lmer(valence ~ block * pos_affectivity + (1|pid), data = per_erp_filter_lat)
summary(mod_valence_pa)
## interaction between valence ratings and positive affectivity

#----- SAVORING THE MOMENT
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_arousal_stm <- lmerTest::lmer(arousal ~ block * savoring_moment + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_stm)
mod_arousal_stm <- lmerTest::lmer(valence ~ block * savoring_moment + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_stm)
## no interactions for savoring the moment

#---- DEPRESSION
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neu_Watch")
mod_arousal_dep <- lmerTest::lmer(arousal ~ depression + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_dep)
# nothing
mod_arousal_dep_block <- lmerTest::lmer(arousal ~ block * depression + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_dep_block)
# nothing
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_valence_dep <- lmerTest::lmer(valence ~ depression + (1|pid), data = per_erp_filter_lat)
summary(mod_valence_dep)
mod_valence_dep_block <- lmerTest::lmer(valence ~ block*depression + (1|pid), data = per_erp_filter_lat)
summary(mod_valence_dep_block)
# nothing
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_arousal_dep_block_neg <- lmerTest::lmer(arousal ~ block * depression + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_dep_block_neg)

#--- ERQ SUBSCALES - LOOK AT VALENCE TOO
# reappraisal arousal
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_arousal_reappraisal <- lmerTest::lmer(arousal ~ erq_reappraisal + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_reappraisal)
mod_arousal_reappraisal_block <- lmerTest::lmer(arousal ~ block*erq_reappraisal + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Neg_Watch", "Neg_Inc", "Neg_Dec")))
summary(mod_arousal_reappraisal_block)
# nothing here
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_arousal_reappraisal_block_pos <- lmerTest::lmer(arousal ~ block*erq_reappraisal + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Pos_Watch", "Pos_Inc", "Pos_Dec")))
summary(mod_arousal_reappraisal_block_pos)
## interactin for erq with pos_dec vs. watch and arousal
# reappraisal valence
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_valence_reappraisal <- lmerTest::lmer(valence ~ erq_reappraisal + (1|pid), data = per_erp_filter_lat)
summary(mod_valence_reappraisal)
mod_valence_reappraisal_block <- lmerTest::lmer(valence ~ block*erq_reappraisal + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Neg_Watch", "Neg_Inc", "Neg_Dec")))
summary(mod_arousal_reappraisal_block)
# interaction between negative increase and erq suppression - not what would be suspected
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_valence_reappraisal_block_pos <- lmerTest::lmer(valence ~ block*erq_reappraisal + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Pos_Watch", "Pos_Inc", "Pos_Dec")))
summary(mod_valence_reappraisal_block_pos)
# intearction between positive decrease and erq reappraisal
## interactin for erq with pos_dec vs. watch and arousal

# suppression - LOOK AT VALENCE???
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_arousal_reappraisal <- lmerTest::lmer(arousal ~ erq_suppression + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_reappraisal)
mod_arousal_reappraisal_block <- lmerTest::lmer(arousal ~ block*erq_suppression + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Neg_Watch", "Neg_Inc", "Neg_Dec")))
summary(mod_arousal_reappraisal_block)
# Interaction between neg inc vs. neg watch and arousal by suppression - doesn't make a whole lot of sense
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_arousal_reappraisal_block_pos <- lmerTest::lmer(arousal ~ block*erq_suppression + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Pos_Watch", "Pos_Inc", "Pos_Dec")))
summary(mod_arousal_reappraisal_block_pos)
# nothing
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_arousal_reappraisal <- lmerTest::lmer(valence ~ erq_suppression + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_reappraisal)
mod_arousal_reappraisal_block <- lmerTest::lmer(arousal ~ block*erq_suppression + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Neg_Watch", "Neg_Inc", "Neg_Dec")))
summary(mod_arousal_reappraisal_block)
# Interaction between neg inc vs. neg watch and arousal by suppression - doesn't make a whole lot of sense
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_arousal_reappraisal_block_pos <- lmerTest::lmer(arousal ~ block*erq_suppression + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Pos_Watch", "Pos_Inc", "Pos_Dec")))
summary(mod_arousal_reappraisal_block_pos)
# nothing

## suppression and valence
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_valence_reappraisal <- lmerTest::lmer(valence ~ erq_suppression + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_reappraisal)
mod_valence_reappraisal_block <- lmerTest::lmer(valence ~ block*erq_suppression + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Neg_Watch", "Neg_Inc", "Neg_Dec")))
summary(mod_valence_reappraisal_block)
# Interaction between neg inc vs. neg watch and arousal by suppression - doesn't make a whole lot of sense

#----- TMMS Subscales
## repair
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neu_Watch")
arousal_repair <- lmerTest::lmer(arousal ~ tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(arousal_repair)
# nothing
arousal_repair_block <- lmerTest::lmer(arousal ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(arousal_repair_block)
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
arousal_repair_block_neg <- lmerTest::lmer(arousal ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(arousal_repair_block_neg)
# interactions between TMMS subscale and neg_watch vs. Neg_dec - cool
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
arousal_repair_block_pos <- lmerTest::lmer(arousal ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(arousal_repair_block_pos)
# nothing for positive
# look at valence 
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neu_Watch")
valence_repair <- lmerTest::lmer(valence ~ tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(valence_repair)
# nothing
valence_repair_block <- lmerTest::lmer(valence ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(valence_repair_block)
# interactions between passive watch conditions here
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
valence_repair_block_neg <- lmerTest::lmer(valence ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(valence_repair_block_neg)
# interactions here between neg ince vs. neg watch and tmms repair
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
valence_repair_block_pos <- lmerTest::lmer(valence ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(valence_repair_block_pos)
# nothing here of interest
## attention
## suppression
```

```{r descriptive statistics}
# sex
per_erp %>% 
  distinct(sex) %>% 
  ungroup() %>% 
  count(sex)

# age
range(per_erp$age)
mean(per_erp$age)
sd(per_erp$age)

# race
per_erp %>% 
  distinct(Race) %>% 
  ungroup() %>% 
  count(Race) %>% 
  mutate(percentage = n / sum(n))

# ethnicity
per_erp %>% 
  distinct(ethnicity) %>% 
  ungroup() %>% 
  count(ethnicity) %>% 
  mutate(percentage = n / sum(n))
