---
title: "Behavioral Ratings and EEG Components"
author: "Ian Kahrilas"
date: "5/19/2020"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lmerTest)
library(here)
library(ggpubr)
library(car)
library(emmeans)
library(easystats)
library(welchADF)
library(moments)
library(modelbased)
library(patchwork)
library(report)
library(r2glmm)
# load in data
per_dat <- read_csv(here("data", "created_data", "per_data_analyses_2020_5_19.csv"))

# create dataset with lateralization variable
tmp <- per_dat %>% 
  pivot_longer(c("EPN_left", "EPN_right"), names_to = "lateralization", names_prefix = "EPN_", values_to = "EPN") %>% 
  select(-c(N170_right, N170_left))
tmp2 <- per_dat %>% 
  pivot_longer(c("N170_left", "N170_right"), names_to = "lateralization", names_prefix = "N170_", values_to = "N170") %>% 
  select(pid, block, N170, lateralization)
per_dat_lat <- left_join(tmp, tmp2, by = c("pid", "block", "lateralization")) %>% 
  select(pid:LPP, EPN, N170, lateralization, everything())

# create bilateral EPN and N170 variable to be used in initial analyses
per_dat <- per_dat %>% 
  mutate(N170 = (N170_left + N170_right) / 2,
         EPN = (EPN_left + EPN_right) / 2) %>% 
  select(pid:LPP, N170, EPN, everything())
```

# EEG and arousal ratings

## LPP and arousal ratings

```{r arousal ratings and LPP}
# LPP
per_dat %>% 
ggplot(., aes(arousal, LPP)) +
  geom_jitter(width = 0.1, height = 0.1) +
  ggtitle("Arousal ratings and LPP") +
  geom_smooth(method = "lm", se = FALSE)

mod_arousal_lpp <- lmer(LPP ~ arousal + (1|pid), data = per_dat)
check_model(mod_arousal_lpp, panel = FALSE)
summary(mod_arousal_lpp)
```

There is a significant relationship between LPP and arousal ratings

## EPN and arousal ratings

```{r arousal ratings and EPN}
# EPN
per_dat %>% 
  ggplot(., aes(arousal, EPN)) +
  geom_jitter(width = 0.1, height = 0.1) +
  ggtitle("Arousal ratings and EPN") +
  geom_smooth(method = "lm", se = FALSE)

mod_arousal_epn <- lmer(EPN ~ arousal + (1|pid), data = per_dat)
check_model(mod_arousal_epn, panel = FALSE)
summary(mod_arousal_epn)
```
  
There is a significant relationship between EPN and arousal ratings

## N170 and arousal ratings

```{r arousal ratings and N170}
# N170
per_dat %>% 
  ggplot(., aes(arousal, N170)) +
  geom_jitter(width = 0.1, height = 0.1) +
  ggtitle("Arousal ratings and N170") +
  geom_smooth(method = "lm", se = FALSE)

mod_arousal_n170 <- lmer(N170 ~ arousal + (1|pid), data = per_dat)
check_model(mod_arousal_n170, panel = FALSE)
summary(mod_arousal_n170)
```

There is a significant relationship between arousal ratings and N170

# EEG and valence ratings

## LPP and valence ratings

```{r valence ratings and LPP, warning=FALSE, message=FALSE}
# LPP
per_dat %>% 
ggplot(., aes(valence, LPP)) +
  geom_jitter(width = 0.1, height = 0.1) + 
  geom_smooth(se = FALSE) +
  ggtitle("Valence ratings and LPP")

mod_valence_lpp <- lmer(LPP ~ poly(valence, 2) + (1|pid), data = per_dat)
check_model(mod_valence_lpp, panel = FALSE)
summary(mod_valence_lpp)
```

There is a significant polynomial relationship between valence and LPP

## EPN and valence ratings

```{r valence ratings and EPN}
# EPN
per_dat  %>% 
ggplot(., aes(valence, EPN)) +
  geom_jitter(width = 0.1, height = 0.1) + 
  geom_smooth(se = FALSE) +
  ggtitle("Valence ratings and EPN")

mod_valence_epn <- lmer(EPN ~ poly(valence, 2) + (1|pid), data = per_dat)
check_model(mod_valence_epn, panel = FALSE)
summary(mod_valence_epn)
```

There is a significant polynomial relationship between valence and EPN

## N170 and valence ratings

```{r}
# N170
per_dat  %>% 
ggplot(., aes(valence, N170)) +
  geom_jitter(width = 0.1, height = 0.1) + 
  geom_smooth(se = FALSE) +
  ggtitle("Valence ratings and N170")

mod_valence_n170 <- lmer(N170 ~ poly(valence, 1) + (1|pid), data = per_dat)
check_model(mod_valence_n170, panel = FALSE)
summary(mod_valence_n170)
```

There is no significant polynomial relationship between N170 and valence, but there is a significant linear relationship, such that increases in N170 are associated with more positive images.

# EEG and difficulty ratings

Scatterplot between LPP and dificulty ratings.

```{r difficulty ratings and LPP, warning=FALSE, message=FALSE}
per_dat %>% 
ggplot(., aes(difficulty, LPP)) +
  geom_jitter(width = 0.1, height = 0.1) + 
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Difficulty ratings and LPP")

lpp_diff <- lmer(LPP ~ difficulty + (1|pid), data = per_dat)
check_model(lpp_diff, panel = FALSE)
summary(lpp_diff)
```

There is a significant linear relationhip between LPP and difficulty ratings

## EPN and difficulty ratings

```{r difficulty ratings and EPN}
per_dat %>% 
ggplot(., aes(difficulty, EPN)) +
  geom_jitter(width = 0.1, height = 0.1) + 
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Difficulty ratings and EPN")

erp_diff <- lmer(EPN ~ difficulty + (1|pid), data = per_dat)
summary(erp_diff)
```

There is a significant linear relationship between difficulty and EPN

## N170 and difficulty ratings
```{r difficulty ratings and N170}
per_dat %>%
ggplot(., aes(difficulty, N170)) +
  geom_jitter(width = 0.1, height = 0.1) + 
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Difficulty ratings and N170")

n170_diff <- lmer(N170 ~ difficulty + (1|pid), data = per_dat)
summary(n170_diff)
```

There is a significant relationship between difficulty ratings and N170

There does appear to be a positive relationship between the difficulty of the task and LPP.

## Valence and difficulty ratings

```{r, message=FALSE, warning=FALSE}
per_erp_filter_lat %>% 
  filter(lateralization == "avg") %>% 
ggplot(., aes(valence, difficulty)) +
  geom_jitter(height = 0.2, width = 0.2) + 
  geom_smooth() +
  ggtitle("Valence and difficulty ratings")
```

There doesn't appear to be a relationship between the two, but we can test this.

```{r, message=FALSE, warning=FALSE}
mod_diff_val <- lmerTest::lmer(difficulty ~ valence + (1|pid), data = per_erp_filter_lat %>% filter(lateralization == "avg"))
summary(mod_diff_val)
mod_diff_val_poly <- lmerTest::lmer(difficulty ~ poly(valence, 2) + (1|pid), data = per_erp_filter_lat %>% filter(lateralization == "avg"))
summary(mod_diff_val_poly) # the polynomial term is non-significant
```

I stand corrected. There is a relationship. Let's check the effect size:

```{r}
r2beta(mod_diff_val)
```

## Valence and arousal

```{r, message=FALSE, warning=FALSE}
per_erp_filter_lat %>% 
  filter(lateralization == "avg") %>% 
ggplot(., aes(valence, arousal)) +
  geom_jitter(width = 0.3, height = 0.3) + 
  geom_smooth() +
#  geom_smooth(method = "lm") +
 # stat_smooth(method = "lm", formula = y ~ poly(x, 2), color = "red") +
  ggtitle("Valence and arousal ratings")
```

It looks like there is a strong curvilinear relationship between the two. 

```{r, message=FALSE, warning=FALSE}
mod_val_arousal <- lmerTest::lmer(arousal ~ poly(valence, 2) + (1|pid), data = per_erp_filter_lat %>% filter(lateralization == "avg"))
summary(mod_val_arousal)
report(mod_val_arousal)
r2beta(mod_val_arousal)
```

The MLM analysis confirms this relationship.

## Arousal and difficulty ratings

```{r, message=FALSE, warning=FALSE}
per_erp_filter_lat %>% 
  filter(lateralization == "avg") %>% 
ggplot(., aes(arousal, difficulty)) +
  geom_jitter(height = 0.3, width = 0.3) + 
  stat_smooth() +
  ggtitle("Arousal and difficulty ratings")
```

There is perhaps a curvilinear relationship. Let's model a locally weighted (green) and polynomial regression (red) line on the plot to see what the relationship is, and how well the polynomial regression line fits compared to the locally weighted one.

```{r, message=FALSE, warning=FALSE}
ggplot(filter(per_erp_filter_lat, lateralization == "avg"), aes(arousal, difficulty)) +
  geom_jitter(height = 0.3, width = 0.3) + 
  geom_smooth(color = "green", alpha = 0.2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 2), color = "red", alpha = 0.2) +
  ggtitle("Arousal and difficulty ratings")
```

It looks like the curvilnear relationship may be a good fit. Let's test it with an MLM analysis

```{r, warning=FALSE, message=FALSE}
mod_diff_arousal <- lmerTest::lmer(difficulty ~ poly(arousal, 2) + (1|pid), data = per_erp_filter_lat %>% filter(lateralization == "avg"))
summary(mod_diff_arousal)
r2beta(mod_diff_arousal)
```

Indeed, the results indicated that the relationship is curvilinear.

Exploration of traits and average EEG components collapsed across all groups.
```{r trait and average eeg exploration}
stm_lpp <- lmerTest::lmer(LPP ~ savoring_moment + lateralization + (1|pid), data = per_erp_filter_lat %>% filter(lateralization %in% c("left", "right")))
summary(stm_lpp)
pa_lpp <- lmerTest::lmer(LPP ~ pos_affectivity + (1|pid), data = per_erp_filter_lat %>% filter(lateralization %in% c("right", "left")))
summary(pa_lpp)
stm_epn <- lmerTest::lmer(EPN ~ savoring_moment + lateralization + (1|pid), data = per_erp_filter_lat %>% filter(lateralization %in% c("left", "right")))
summary(stm_epn)
pa_epn <- lmerTest::lmer(EPN ~ pos_affectivity + (1|pid), data = per_erp_filter_lat %>% filter(lateralization %in% c("left", "right")))
summary(pa_epn)
# revised lpp
stm_lpp_rev <- lmerTest::lmer(LPP ~ savoring_moment + (1|pid), data = per_erp_rev)
summary(stm_lpp_rev)
pa_lpp_rev <- lmerTest::lmer(LPP ~ pos_affectivity + (1|pid), data = per_erp_rev)
summary(pa_lpp_rev)
# right front
stm_front <- lmerTest::lmer(front_avr ~ savoring_moment*lateralization + (1|pid), data = per_erp_filter_lat %>%  filter(lateralization %in% c("right", "left")))
summary(stm_front)

stm_right_front <- lmerTest::lmer(front_avr ~ depression + (1|pid), data = per_erp_filter_lat %>% filter(lateralization %in% c("right")))
summary(stm_right_front)
```

# check out arousal/valence predicted by block/personality traits
## CONTINUE WITH THIS SECTION
```{r}
#---- POS_AFFECTIVITY
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neu_Watch")
mod_arousal_pa <- lmerTest::lmer(arousal ~ block * pos_affectivity + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_pa)
## interaction between arousal ratings and positive affecitivity
mod_valence_pa <- lmerTest::lmer(valence ~ block * pos_affectivity + (1|pid), data = per_erp_filter_lat)
summary(mod_valence_pa)
## interaction between valence ratings and positive affectivity

#----- SAVORING THE MOMENT
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_arousal_stm <- lmerTest::lmer(arousal ~ block * savoring_moment + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_stm)
mod_arousal_stm <- lmerTest::lmer(valence ~ block * savoring_moment + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_stm)
## no interactions for savoring the moment

#---- DEPRESSION
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neu_Watch")
mod_arousal_dep <- lmerTest::lmer(arousal ~ depression + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_dep)
# nothing
mod_arousal_dep_block <- lmerTest::lmer(arousal ~ block * depression + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_dep_block)
# nothing
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_valence_dep <- lmerTest::lmer(valence ~ depression + (1|pid), data = per_erp_filter_lat)
summary(mod_valence_dep)
mod_valence_dep_block <- lmerTest::lmer(valence ~ block*depression + (1|pid), data = per_erp_filter_lat)
summary(mod_valence_dep_block)
# nothing
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_arousal_dep_block_neg <- lmerTest::lmer(arousal ~ block * depression + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_dep_block_neg)

#--- ERQ SUBSCALES - LOOK AT VALENCE TOO
# reappraisal arousal
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_arousal_reappraisal <- lmerTest::lmer(arousal ~ erq_reappraisal + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_reappraisal)
mod_arousal_reappraisal_block <- lmerTest::lmer(arousal ~ block*erq_reappraisal + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Neg_Watch", "Neg_Inc", "Neg_Dec")))
summary(mod_arousal_reappraisal_block)
# nothing here
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_arousal_reappraisal_block_pos <- lmerTest::lmer(arousal ~ block*erq_reappraisal + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Pos_Watch", "Pos_Inc", "Pos_Dec")))
summary(mod_arousal_reappraisal_block_pos)
## interactin for erq with pos_dec vs. watch and arousal
# reappraisal valence
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_valence_reappraisal <- lmerTest::lmer(valence ~ erq_reappraisal + (1|pid), data = per_erp_filter_lat)
summary(mod_valence_reappraisal)
mod_valence_reappraisal_block <- lmerTest::lmer(valence ~ block*erq_reappraisal + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Neg_Watch", "Neg_Inc", "Neg_Dec")))
summary(mod_arousal_reappraisal_block)
# interaction between negative increase and erq suppression - not what would be suspected
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_valence_reappraisal_block_pos <- lmerTest::lmer(valence ~ block*erq_reappraisal + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Pos_Watch", "Pos_Inc", "Pos_Dec")))
summary(mod_valence_reappraisal_block_pos)
# intearction between positive decrease and erq reappraisal
## interactin for erq with pos_dec vs. watch and arousal

# suppression - LOOK AT VALENCE???
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_arousal_reappraisal <- lmerTest::lmer(arousal ~ erq_suppression + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_reappraisal)
mod_arousal_reappraisal_block <- lmerTest::lmer(arousal ~ block*erq_suppression + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Neg_Watch", "Neg_Inc", "Neg_Dec")))
summary(mod_arousal_reappraisal_block)
# Interaction between neg inc vs. neg watch and arousal by suppression - doesn't make a whole lot of sense
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_arousal_reappraisal_block_pos <- lmerTest::lmer(arousal ~ block*erq_suppression + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Pos_Watch", "Pos_Inc", "Pos_Dec")))
summary(mod_arousal_reappraisal_block_pos)
# nothing
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_arousal_reappraisal <- lmerTest::lmer(valence ~ erq_suppression + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_reappraisal)
mod_arousal_reappraisal_block <- lmerTest::lmer(arousal ~ block*erq_suppression + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Neg_Watch", "Neg_Inc", "Neg_Dec")))
summary(mod_arousal_reappraisal_block)
# Interaction between neg inc vs. neg watch and arousal by suppression - doesn't make a whole lot of sense
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
mod_arousal_reappraisal_block_pos <- lmerTest::lmer(arousal ~ block*erq_suppression + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Pos_Watch", "Pos_Inc", "Pos_Dec")))
summary(mod_arousal_reappraisal_block_pos)
# nothing

## suppression and valence
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
mod_valence_reappraisal <- lmerTest::lmer(valence ~ erq_suppression + (1|pid), data = per_erp_filter_lat)
summary(mod_arousal_reappraisal)
mod_valence_reappraisal_block <- lmerTest::lmer(valence ~ block*erq_suppression + (1|pid), data = filter(per_erp_filter_lat, block %in% c("Neg_Watch", "Neg_Inc", "Neg_Dec")))
summary(mod_valence_reappraisal_block)
# Interaction between neg inc vs. neg watch and arousal by suppression - doesn't make a whole lot of sense

#----- TMMS Subscales
## repair
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neu_Watch")
arousal_repair <- lmerTest::lmer(arousal ~ tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(arousal_repair)
# nothing
arousal_repair_block <- lmerTest::lmer(arousal ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(arousal_repair_block)
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
arousal_repair_block_neg <- lmerTest::lmer(arousal ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(arousal_repair_block_neg)
# interactions between TMMS subscale and neg_watch vs. Neg_dec - cool
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
arousal_repair_block_pos <- lmerTest::lmer(arousal ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(arousal_repair_block_pos)
# nothing for positive
# look at valence 
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neu_Watch")
valence_repair <- lmerTest::lmer(valence ~ tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(valence_repair)
# nothing
valence_repair_block <- lmerTest::lmer(valence ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(valence_repair_block)
# interactions between passive watch conditions here
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Neg_Watch")
valence_repair_block_neg <- lmerTest::lmer(valence ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(valence_repair_block_neg)
# interactions here between neg ince vs. neg watch and tmms repair
per_erp_filter_lat$block <- relevel(per_erp_filter_lat$block, "Pos_Watch")
valence_repair_block_pos <- lmerTest::lmer(valence ~ block*tmms_repair + (1|pid), data = per_erp_filter_lat)
summary(valence_repair_block_pos)
# nothing here of interest
## attention
## suppression
```

```{r descriptive statistics}
# sex
per_erp %>% 
  distinct(sex) %>% 
  ungroup() %>% 
  count(sex)

# age
range(per_erp$age)
mean(per_erp$age)
sd(per_erp$age)

# race
per_erp %>% 
  distinct(Race) %>% 
  ungroup() %>% 
  count(Race) %>% 
  mutate(percentage = n / sum(n))

# ethnicity
per_erp %>% 
  distinct(ethnicity) %>% 
  ungroup() %>% 
  count(ethnicity) %>% 
  mutate(percentage = n / sum(n))
