---
title: "Behavioral Ratings and EEG Components"
author: "Ian Kahrilas"
date: "5/19/2020"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lmerTest)
library(here)
library(ggpubr)
library(car)
library(emmeans)
library(easystats)
library(welchADF)
library(moments)
library(modelbased)
library(patchwork)
library(report)
library(r2glmm)
# load in data
per_dat <- read_csv(here("data", "created_data", "per_data_analyses_2020_5_19.csv"))

# create dataset with lateralization variable
tmp <- per_dat %>% 
  pivot_longer(c("EPN_left", "EPN_right"), names_to = "lateralization", names_prefix = "EPN_", values_to = "EPN") %>% 
  select(-c(N170_right, N170_left))
tmp2 <- per_dat %>% 
  pivot_longer(c("N170_left", "N170_right"), names_to = "lateralization", names_prefix = "N170_", values_to = "N170") %>% 
  select(pid, block, N170, lateralization)
per_dat_lat <- left_join(tmp, tmp2, by = c("pid", "block", "lateralization")) %>% 
  select(pid:LPP, EPN, N170, lateralization, everything())

# create bilateral EPN and N170 variable to be used in initial analyses
per_dat <- per_dat %>% 
  mutate(N170 = (N170_left + N170_right) / 2,
         EPN = (EPN_left + EPN_right) / 2) %>% 
  select(pid:LPP, N170, EPN, everything())
```

# EEG and arousal ratings

## LPP and arousal ratings

```{r arousal ratings and LPP}
# LPP
per_dat %>% 
ggplot(., aes(arousal, LPP)) +
  geom_jitter(width = 0.1, height = 0.1) +
  ggtitle("Arousal ratings and LPP") +
  geom_smooth(method = "lm", se = FALSE)

mod_arousal_lpp <- lmer(LPP ~ arousal + (1|pid), data = per_dat)
check_model(mod_arousal_lpp, panel = FALSE)
summary(mod_arousal_lpp)
```

There is a significant relationship between LPP and arousal ratings

## EPN and arousal ratings

```{r arousal ratings and EPN}
# EPN
per_dat %>% 
  ggplot(., aes(arousal, EPN)) +
  geom_jitter(width = 0.1, height = 0.1) +
  ggtitle("Arousal ratings and EPN") +
  geom_smooth(method = "lm", se = FALSE)

mod_arousal_epn <- lmer(EPN ~ arousal + (1|pid), data = per_dat)
check_model(mod_arousal_epn, panel = FALSE)
summary(mod_arousal_epn)
```
  
There is a significant relationship between EPN and arousal ratings

## N170 and arousal ratings

```{r arousal ratings and N170}
# N170
per_dat %>% 
  ggplot(., aes(arousal, N170)) +
  geom_jitter(width = 0.1, height = 0.1) +
  ggtitle("Arousal ratings and N170") +
  geom_smooth(method = "lm", se = FALSE)

mod_arousal_n170 <- lmer(N170 ~ arousal + (1|pid), data = per_dat)
check_model(mod_arousal_n170, panel = FALSE)
summary(mod_arousal_n170)
```

There is a significant relationship between arousal ratings and N170

# EEG and valence ratings

## LPP and valence ratings

```{r valence ratings and LPP, warning=FALSE, message=FALSE}
# LPP
per_dat %>% 
ggplot(., aes(valence, LPP)) +
  geom_jitter(width = 0.1, height = 0.1) + 
  geom_smooth(se = FALSE) +
  ggtitle("Valence ratings and LPP")

mod_valence_lpp <- lmer(LPP ~ poly(valence, 2) + (1|pid), data = per_dat)
check_model(mod_valence_lpp, panel = FALSE)
summary(mod_valence_lpp)
```

There is a significant polynomial relationship between valence and LPP

## EPN and valence ratings

```{r valence ratings and EPN}
# EPN
per_dat  %>% 
ggplot(., aes(valence, EPN)) +
  geom_jitter(width = 0.1, height = 0.1) + 
  geom_smooth(se = FALSE) +
  ggtitle("Valence ratings and EPN")

mod_valence_epn <- lmer(EPN ~ poly(valence, 2) + (1|pid), data = per_dat)
check_model(mod_valence_epn, panel = FALSE)
summary(mod_valence_epn)
```

There is a significant polynomial relationship between valence and EPN

## N170 and valence ratings

```{r}
# N170
per_dat  %>% 
ggplot(., aes(valence, N170)) +
  geom_jitter(width = 0.1, height = 0.1) + 
  geom_smooth(se = FALSE) +
  ggtitle("Valence ratings and N170")

mod_valence_n170 <- lmer(N170 ~ poly(valence, 1) + (1|pid), data = per_dat)
check_model(mod_valence_n170, panel = FALSE)
summary(mod_valence_n170)
```

There is no significant polynomial relationship between N170 and valence, but there is a significant linear relationship, such that increases in N170 are associated with more positive images.

# EEG and difficulty ratings

Scatterplot between LPP and dificulty ratings.

```{r difficulty ratings and LPP, warning=FALSE, message=FALSE}
per_dat %>% 
ggplot(., aes(difficulty, LPP)) +
  geom_jitter(width = 0.1, height = 0.1) + 
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Difficulty ratings and LPP")

lpp_diff <- lmer(LPP ~ difficulty + (1|pid), data = per_dat)
check_model(lpp_diff, panel = FALSE)
summary(lpp_diff)
```

There is a significant linear relationhip between LPP and difficulty ratings

## EPN and difficulty ratings

```{r difficulty ratings and EPN}
per_dat %>% 
ggplot(., aes(difficulty, EPN)) +
  geom_jitter(width = 0.1, height = 0.1) + 
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Difficulty ratings and EPN")

erp_diff <- lmer(EPN ~ difficulty + (1|pid), data = per_dat)
summary(erp_diff)
```

There is a significant linear relationship between difficulty and EPN

## N170 and difficulty ratings
```{r difficulty ratings and N170}
per_dat %>%
ggplot(., aes(difficulty, N170)) +
  geom_jitter(width = 0.1, height = 0.1) + 
  geom_smooth(method = "lm", se = FALSE) +
  ggtitle("Difficulty ratings and N170")

n170_diff <- lmer(N170 ~ difficulty + (1|pid), data = per_dat)
summary(n170_diff)
```

There is a significant relationship between difficulty ratings and N170
