---
title: "PER Passive Block and EEG Component Analyses"
author: "Ian Kahrilas"
date: "5/15/2020"
output: pdf_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lmerTest)
library(here)
library(ggpubr)
library(car)
library(emmeans)
library(easystats)
library(welchADF)
library(moments)
library(modelbased)
library(patchwork)
library(report)
library(r2glmm)
# load in data
per_dat <- read_csv(here("data", "created_data", "per_data_analyses_2020_5_19.csv"))
```

# Characterizing relationship between block conditions and EEG components

## Passive conditions and LPP

```{r LPP by passive block, warning=FALSE, message=FALSE}
# box and whisker plots for LPP
per_dat %>% 
  filter(block %in% c("Neg_Watch", "Neu_Watch", "Pos_Watch")) %>% 
  mutate(block = fct_relevel(block, c("Neg_Watch", 
                                      "Neu_Watch",
                                      "Pos_Watch"))) %>% # Change block order
  ggplot(., aes(block, LPP)) +
  geom_boxplot() + 
  ggtitle("LPP box and whisker plots for passive blocks")

per_dat$block <- relevel(as.factor(per_dat$block), "Neu_Watch")
passive_lpp_mod <- lmer(LPP ~ block + (1|pid), data = per_dat %>% filter(block %in% c("Neg_Watch", "Neu_Watch", "Pos_Watch")))
# check the quality of the model
check_model(passive_lpp_mod, panel = FALSE)
summary(passive_lpp_mod)
r2beta(passive_lpp_mod)
report(passive_lpp_mod)
```

There are significant differences in LPP for each passive block

## Passive conditions and EPN (right and left)

```{r}
# create dataset with lateralization variable
tmp <- per_dat %>% 
  pivot_longer(c("EPN_left", "EPN_right"), names_to = "lateralization", names_prefix = "EPN_", values_to = "EPN") %>% 
  select(-c(N170_right, N170_left))
tmp2 <- per_dat %>% 
  pivot_longer(c("N170_left", "N170_right"), names_to = "lateralization", names_prefix = "N170_", values_to = "N170") %>% 
  select(pid, block, N170, lateralization)
per_dat_lat <- left_join(tmp, tmp2, by = c("pid", "block", "lateralization")) %>% 
  select(pid:LPP, EPN, N170, lateralization, everything())

# create bilateral EPN and N170 variable to be used in initial analyses
per_dat <- per_dat %>% 
  mutate(N170 = (N170_left + N170_right) / 2,
         EPN = (EPN_left + EPN_right) / 2) %>% 
  select(pid:LPP, N170, EPN, everything())

# box and whisker plots for EPN
per_dat %>% 
  filter(block %in% c("Neg_Watch", "Neu_Watch", "Pos_Watch")) %>% 
  mutate(block = fct_relevel(block, c("Neg_Watch",
                                      "Neu_Watch",
                                      "Pos_Watch"))) %>% # Change block order 
  ggplot(., aes(block, EPN)) +
  geom_boxplot() +
  ggtitle("EPN box and whisker plots for each block")

# fit model
passive_epn_mod <- lmer(EPN ~ block + (1|pid), data = per_dat %>% filter(block %in% c("Neg_Watch", "Neu_Watch", "Pos_Watch")))
# check the quality of the model
check_model(passive_epn_mod, panel = FALSE)
summary(passive_epn_mod)
r2beta(passive_epn_mod)
report(passive_epn_mod)
```

There are significant differences in EPN for each passive block

## Passive conditions and N170 (right and left)

```{r}
# box and whisker plots for EPN
per_dat %>% 
  filter(block %in% c("Neg_Watch", "Neu_Watch", "Pos_Watch")) %>% 
  mutate(block = fct_relevel(block, c("Neg_Watch",
                                      "Neu_Watch",
                                      "Pos_Watch"))) %>% # Change block order 
  ggplot(., aes(block, N170)) +
  geom_boxplot() +
  ggtitle("N170 box and whisker plots for each block")

# fit model
passive_n170_mod <- lmer(N170 ~ block + (1|pid), data = per_dat %>% filter(block %in% c("Neg_Watch", "Neu_Watch", "Pos_Watch")))
# check the quality of the model
check_model(passive_n170_mod, panel = FALSE)
summary(passive_n170_mod)
r2beta(passive_n170_mod)
report(passive_n170_mod)
```

There are significant differences in N170 for each passive block
