---
title: "Regulation Block EEG Component Analyses"
author: "Ian Kahrilas"
date: "5/19/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lmerTest)
library(here)
library(ggpubr)
library(car)
library(emmeans)
library(easystats)
library(welchADF)
library(moments)
library(modelbased)
library(patchwork)
library(report)
library(r2glmm)
# load in data
per_dat <- read_csv(here("data", "created_data", "per_data_analyses_2020_5_19.csv"))

# create dataset with lateralization variable
tmp <- per_dat %>% 
  pivot_longer(c("EPN_left", "EPN_right"), names_to = "lateralization", names_prefix = "EPN_", values_to = "EPN") %>% 
  select(-c(N170_right, N170_left))
tmp2 <- per_dat %>% 
  pivot_longer(c("N170_left", "N170_right"), names_to = "lateralization", names_prefix = "N170_", values_to = "N170") %>% 
  select(pid, block, N170, lateralization)
per_dat_lat <- left_join(tmp, tmp2, by = c("pid", "block", "lateralization")) %>% 
  select(pid:LPP, EPN, N170, lateralization, everything())

# create bilateral EPN and N170 variable to be used in initial analyses
per_dat <- per_dat %>% 
  mutate(N170 = (N170_left + N170_right) / 2,
         EPN = (EPN_left + EPN_right) / 2) %>% 
  select(pid:LPP, N170, EPN, everything())
```

# Characterizing relationship between regulation block conditions and EEG components

## Positive Regulation conditions and LPP

```{r LPP by passive block, warning=FALSE, message=FALSE}
# box and whisker plots for LPP and positive conditions
per_dat %>% 
  filter(block %in% c("Pos_Watch", "Pos_Dec", "Pos_Inc")) %>% 
  mutate(block = fct_relevel(block, c("Pos_Watch", 
                                      "Pos_Dec",
                                      "Pos_Inc"))) %>% # Change block order
  ggplot(., aes(block, LPP)) +
  geom_boxplot() + 
  ggtitle("LPP box and whisker plots for positive regulation blocks")

per_dat$block <- relevel(as.factor(per_dat$block), "Pos_Watch")
positive_lpp_mod <- lmer(LPP ~ block + (1|pid), data = per_dat)
# check the quality of the model
check_model(positive_lpp_mod, panel = FALSE)
summary(positive_lpp_mod)
r2beta(positive_lpp_mod)
report(positive_lpp_mod)

pairs(emmeans(positive_lpp_mod, "block"))
summary(aov(LPP ~ block, data = per_dat))
```

There are no significant differences in LPP for each positive block

## Positive conditions and EPN

```{r}
per_dat %>% 
  filter(block %in% c("Pos_Watch", "Pos_Dec", "Pos_Inc")) %>% 
  mutate(block = fct_relevel(block, c("Pos_Watch", 
                                      "Pos_Dec",
                                      "Pos_Inc"))) %>% # Change block order
  ggplot(., aes(block, EPN)) +
  geom_boxplot() + 
  ggtitle("EPN box and whisker plots for positive regulation blocks")

per_dat$block <- relevel(as.factor(per_dat$block), "Pos_Watch")
positive_epn_mod <- lmer(EPN ~ block + (1|pid), data = per_dat)
# check the quality of the model
check_model(positive_epn_mod, panel = FALSE)
summary(positive_epn_mod)
r2beta(positive_epn_mod)
report(positive_epn_mod)
```

There are strong differences between the positive increase and positive watch condition for EPN

## Positive conditions and N170

```{r}
per_dat %>% 
  filter(block %in% c("Pos_Watch", "Pos_Dec", "Pos_Inc")) %>% 
  mutate(block = fct_relevel(block, c("Pos_Watch", 
                                      "Pos_Dec",
                                      "Pos_Inc"))) %>% # Change block order
  ggplot(., aes(block, N170)) +
  geom_boxplot() + 
  ggtitle("N170 box and whisker plots for positive regulation blocks")

per_dat$block <- relevel(as.factor(per_dat$block), "Pos_Watch")
positive_n170_mod <- lmer(N170 ~ block + (1|pid), data = per_dat)
# check the quality of the model
check_model(positive_n170_mod, panel = FALSE)
summary(positive_n170_mod)
r2beta(positive_n170_mod)
report(positive_n170_mod)
```

There aresignificant differences between positive watch and positive increase, though likely won't withstand multiple-comparison adjustments.

## Negative regulation conditions and LPP

```{r}
# box and whisker plots for LPP and positive conditions
per_dat %>% 
  filter(block %in% c("Neg_Watch", "Neg_Dec", "Neg_Inc")) %>% 
  mutate(block = fct_relevel(block, c("Neg_Watch", 
                                      "Neg_Dec",
                                      "Neg_Inc"))) %>% # Change block order
  ggplot(., aes(block, LPP)) +
  geom_boxplot() + 
  ggtitle("LPP box and whisker plots for positive regulation blocks")

per_dat$block <- relevel(as.factor(per_dat$block), "Neg_Watch")
negative_lpp_mod <- lmer(LPP ~ block + (1|pid), data = per_dat)
# check the quality of the model
check_model(negative_lpp_mod, panel = FALSE)
summary(negative_lpp_mod)
r2beta(negative_lpp_mod)
report(negative_lpp_mod)
```

There are significant differences in LPP between the negative watch and negative increase conditions

## Negative regulation conditions and EPN

```{r}
# box and whisker plots for LPP and positive conditions
per_dat %>% 
  filter(block %in% c("Neg_Watch", "Neg_Dec", "Neg_Inc")) %>% 
  mutate(block = fct_relevel(block, c("Neg_Watch", 
                                      "Neg_Dec",
                                      "Neg_Inc"))) %>% # Change block order
  ggplot(., aes(block, EPN)) +
  geom_boxplot() + 
  ggtitle("EPN box and whisker plots for positive regulation blocks")

per_dat$block <- relevel(as.factor(per_dat$block), "Neg_Watch")
negative_epn_mod <- lmer(EPN ~ block + (1|pid), data = per_dat)
# check the quality of the model
check_model(negative_epn_mod, panel = FALSE)
summary(negative_epn_mod)
r2beta(negative_epn_mod)
report(negative_epn_mod)
```

There are no differences in EPN for the negative regulation blocks

## Negative regulation conditions and N170

```{r}
# box and whisker plots for LPP and positive conditions
per_dat %>% 
  filter(block %in% c("Neg_Watch", "Neg_Dec", "Neg_Inc")) %>% 
  mutate(block = fct_relevel(block, c("Neg_Watch", 
                                      "Neg_Dec",
                                      "Neg_Inc"))) %>% # Change block order
  ggplot(., aes(block, N170)) +
  geom_boxplot() + 
  ggtitle("N170 box and whisker plots for positive regulation blocks")

per_dat$block <- relevel(as.factor(per_dat$block), "Neg_Watch")
negative_n170_mod <- lmer(N170 ~ block + (1|pid), data = per_dat)
# check the quality of the model
check_model(negative_n170_mod, panel = FALSE)
summary(negative_n170_mod)
r2beta(negative_n170_mod)
report(negative_n170_mod)
```

No differences in N70 among negative regulation conditions

# Single model looking at all differences with pairwise comparisons

```{r}
# single emm model for all conditions
per_dat_cond <- per_dat %>% 
  separate(block, c("valence", "regulation"), "_") %>% 
  mutate(valence_condition = if_else(valence == "Neg", "Negative",
                           if_else(valence == "Pos", "Positive", "Neutral")),
         regulation_condition = if_else(regulation == "Dec", "Decrease",
                              if_else(regulation == "Inc", "Increase", "Watch")))

# LPP comparisons
reg_mod_lpp <- lmer(LPP ~ valence_condition * regulation_condition + (1|pid), data = per_dat_cond)
emmeans(reg_mod_lpp, pairwise ~ valence_condition | regulation_condition)
emmeans(reg_mod_lpp, pairwise ~ regulation_condition | valence_condition)

# EPN comparisons
reg_mod_epn <- lmer(EPN ~ valence_condition * regulation_condition + (1|pid), data = per_dat_cond)
emmeans(reg_mod_epn, pairwise ~ valence_condition | regulation_condition)
emmeans(reg_mod_epn, pairwise ~ regulation_condition | valence_condition)

# N170 comparisons
reg_mod_n170 <- lmer(N170 ~ valence_condition * regulation_condition + (1|pid), data = per_dat_cond)
emmeans(reg_mod_n170, pairwise ~ valence_condition | regulation_condition)
confint(emmeans(reg_mod_n170, pairwise ~ regulation_condition | valence_condition), )
?confint
```
